Fast Algorithms for Intersection of Non-matching Grids Using \plucker Coordinates.

### 2016-10-01 paper_intersections.tex

\section{Global Mesh Intersection Algorithm}
\label{sec:front_advancing}
Having the algorithms for element-element intersections we can proceed to the mesh intersection algorithm. 
We first compute all component-bulk mesh intersections that is (1d-3d and 2d-3d) and then the 1d-2d and 2d-2d intersections using the 3d mesh to get the intersection pair candidates.
Element intersections for the particular component and bulk mesh 
are obtained in two phases: firstly, we look for the first two elements intersecting each other (initialization); 
secondly, we prolong the intersection by investigating neighbouring elements (front tracking).
\noteJB{Not sure that "prolong" is the right verb.}

@@

\paragraph{Initialization}
We choose an arbitrary element of the component mesh and check its intersection with all elements of the bulk mesh.
This process is accelerated by computing the axis aligned bounding box (AABB) for every element and use intersection of the bounding boxes
as a fast indicator for possible intersection of the elements. This step takes $O(N)$ time with respect to the number of elements of the bulk mesh $N$.
If the number of components $k$ is small and if the components are contained inside the bulk mesh, the total time of initialization may still be linear $O(kn)$ \notePE{I believe you ment $O(kN)$ here}. However,
for more complex cases we organize the bounding boxes of the bulk mesh into the bounding interval hierarchy (BIH) \cite{EGWR:EGSR06:139-149},
a data structure in principle equivalent 
to R-trees \cite{guttman_r-trees:_1984}, \cite{nam_comparative_2004}. The creation time is $O(N\log(N/n))$ and the lookup time $O(\log(N/n))$ where $n$ is number
of the bulk elements in the leaf nodes of the tree.

\paragraph{Advancing Front Method}
The advancing front method requires the neigbouring information for the elements within the components as well as within the bulk mesh.
It can be viewed as the breadth first search algorithm for a graph which vertices are intersection polygons and edges are sides shared by
two polygons. Since every side of IP is on the boundary of either component or bulk element, we can distinguish the bulk and component edges. Correspondingly, we save new candidate pairs into a~\emph{bulk queue} or 
a~\emph{component queue} to be subsequently processed later.
The scheme of the advancing front algorithm is displayed by the scheme in \fig{fig:prolongation},
where the queues are represented by the yellow boxes.
%
\begin{figure}[!htb]
%   \vspace{0pt}
  \centering    
    \includegraphics[width=\textwidth]{\figpath prolongation_scheme_ip_new.pdf}
  \caption{Advancing front algorithm for 1d-2d and 2d-3d intersections.}
  \label{fig:prolongation}
\end{figure}

>>>>

\section{Global Mesh Intersection Algorithm}
\label{sec:front_advancing}
Having the algorithms for element-element intersections at our disposal we can proceed to the mesh intersection algorithm. 
We consider the composed mesh $\mathcal T$ containing the 3d mesh $\mathcal T_1$ that we shall call a bulk mesh $\mathcal T_b$. Any other 
mesh $\mathcal T_i$, with dimensions $d_i < 3$, $i=1,\dots, N_{\mathcal T}$ we shall call a component mesh. 
We first compute all component-bulk mesh intersections that is (1d-3d and 2d-3d) using the advancing front algorithm which is described in Sections 
\ref{sec:initialization}, \ref{sec:front} and then the 1d-2d and 2d-2d 
intersections use the bulk mesh to get the intersection pair candidates, the Section \ref{sec:compnents}.

Let us consider a single pair of the component mesh $\mathcal T_c$ and the bulk mesh $\mathcal T_b$. 
Element intersections for this pair of meshes are obtained in two phases: firstly, we look for the first two elements intersecting each other (initialization); 
secondly, we prolong the intersection by investigating neighbouring elements (front tracking).
\noteJB{Not sure that "prolong" is the right verb.}

@@

\subsection{Initialization}
\label{sec:initialization}
\noteJB{Possibly move this afte Advancing front section since it is in fact single step in the main loop.}
We choose an arbitrary element of the component mesh and check its intersection with all elements of the bulk mesh.
This process is accelerated by computing the axis aligned bounding box (AABB) for every element and use intersection of the bounding boxes
as a fast indicator for possible intersection of the elements. This step takes $O(N)$ time with respect to the number of elements of the bulk mesh $N$.
If the number of components $k$ is small and if the components are contained inside the bulk mesh, the total time of initialization may still be linear $O(kN)$. However,
for more complex cases we organize the bounding boxes of the bulk mesh into the bounding interval hierarchy (BIH) \cite{EGWR:EGSR06:139-149},
a data structure in principle equivalent 
to R-trees \cite{guttman_r-trees:_1984}, \cite{nam_comparative_2004}. The creation time is $O(N\log(N/n))$ and the lookup time $O(\log(N/n))$ where $n$ is number
of the bulk elements in the leaf nodes of the tree.

\subsection{Advancing Front Method}
\label{front}
The advancing front algorithm requires the neigbouring information for the elements within the component mesh $\mathcal T_c$ 
as well as within the bulk mesh $\mathcal T_b$. It can be viewed as the breadth first search algorithm for a graph where graph vertices are 
intersection polygons and graph edges are sides shared by two polygons. Since every side of IP is on the boundary of either 
the component element or the bulk element, we can distinguish bulk and component edges. 
Correspondingly the candidate paris are enqueued into \emph{component queue} $Q_c$ and the \emph{bulk queue} $Q_b$, respectively.

\begin{algorithm}
  \caption{Advancing front algorithm}  
  \label{algo:advancing front}

  \SetKw{return}{return}
  \SetKw{edgefaces}{edge faces}
  \DontPrintSemicolon
  %\KwIn{vertex $v$ of $S_3$, $L[:]$ intersection results for edges of $S_3$}
  %\KwOut{$(x_1, x_2)$, $x_1, x_2 \in M_3$, coincident with $v$ and intersected by the plane of $S_2$}
  mark all $c\in \mathcal T_c$ unvisited\;
  \For{unvisited $c\in\mathcal T_c$}{
    mark $c$ visited\;
    find list $L$ of intersection candidates\;
    append $L$ to queue $Q_c$\;
    \For{$(c, b) \in Q_c$}{
        mark $c$ visited\;
        push $(c,b)$ into $Q_b$\;
        \For{$(c, b) \in Q_b$}{            
            list $I$ of ICs of $(c,b)$ intersection\;
            \For{$p\in I$}{
                \If{$p$ on boundary of $c$}{
                    get neighbours $C'$\;
                    \tcp{check pair if unvisited, mark visited}
                    enqueue $(c', b)$ into $Q_c$ for all $c'\in C'$ 
                }
                \If{$p$ on boundary of $b$}{
                    get neighbours $B'$\;
                    \If{$B'$ is empty and not on boundary of $c$}{mark $c$ unvisited}
                    enqueue $(c, b')$ into $Q_b$ for all $b'\in B'$ 
                }                
                \noteJB{Questionable}\;
                \If{$p$ on both boundaries}{
                    enqueue $(c', b')$ into $Q_c$ for all $b'\in B',\ c'\in C'$ 
                }
            }

        }
    }
  }

\end{algorithm}

%
\begin{figure}[!htb]
%   \vspace{0pt}
  \centering    
    \includegraphics[width=\textwidth]{\figpath prolongation_scheme_ip_new.pdf}
  \caption{Advancing front algorithm for 1d-2d and 2d-3d intersections.}
  \label{fig:prolongation}
\end{figure}

First, we mark all component elements $c\in\mathcal T_c$ unvisited. The for every unvisited element $c\in \mathcal T_c$, we mark it visited
then find intersection candidate pair $(c,b)$, $b\in\mathcal T_b$ 
and initialize the front tracking for every unvisited .
